Blue Hunters: Bluetooth RSSI Locator Robots

### 2018-02-01 article/article.tex
Fluff introduction + remove local refs

We built 2 small cars which used Bluetooth Received Signal Strength
Indicator (RSSI) measurements to navigate towards a stationary base
station. The cars and base station used a Bluetooth Low Energy (BLE) 4.0
module to take the measurements and a PIC32MX250 microcontroller. The
cars also used a 3 axis magnetometer as as compass in order to reliably
turn, as well as 2 micro 9 g servos to drive. Each unit was powered with
3 AA batteries. Finally, the chassis and wheels of each car were 3D
printed.

@@

>>>>

Position estimation and navigation for robots is an interesting problem
in the field of robotics. We investigate the challenge of determining
relative position using signal strength; by placing a moving robot on
the same plane as a beacon, oriented and positioned randomly, the
robot can hunt out and move towards the beacon by itself. We discuss 
our procedures and challenges we encountered in this article.

Specifically, we built 2 small cars which used Bluetooth Received Signal Strength
Indicator (RSSI) measurements to navigate towards a stationary base
station. The cars and base station used a Bluetooth Low Energy (BLE) 4.0
module to take the measurements and a PIC32MX250 microcontroller. The
cars also used a 3 axis magnetometer as as compass in order to reliably
turn, as well as 2 micro 9 g servos to drive. Each unit was powered with
3 AA batteries. Finally, the chassis and wheels of each car were 3D
printed.

@@

The design of the project can be split into 3 main parts: the chassis, the electronics (hardware), and the software. The following sections discuss implementation details.
